\documentclass[11pt]{article}

\input{glyphtounicode}
\pdfgentounicode=1
\ifdefined\pdfinterwordspaceon
  \pdfinterwordspaceon
\fi

\usepackage[utf8]{inputenc}
\usepackage{cmap}
\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage{microtype}
\usepackage{amsmath,amssymb}
\usepackage{graphicx}
\usepackage{float}
\usepackage{booktabs}
\usepackage{array}
\usepackage{longtable}
\usepackage{enumitem}
\usepackage{xcolor}
\usepackage[font=small,justification=raggedright,singlelinecheck=false]{caption}
\usepackage{url}
\usepackage{indentfirst}
\usepackage{flafter}
\usepackage{placeins}
\usepackage{needspace}
% Temporary author-year citation mode for final manual reference verification.
% For arXiv numeric submission, switch back to:
% \usepackage[numbers,sort&compress]{natbib}
% \bibliographystyle{unsrtnat}
\usepackage[authoryear,round]{natbib}
\setlength{\bibsep}{2pt plus 0.3ex}
\usepackage[colorlinks=true,linkcolor=blue,citecolor=blue,urlcolor=blue]{hyperref}
\usepackage[nameinlink,capitalise,noabbrev]{cleveref}

% arXiv submission plan: primary cs.SE; cross-list cs.AI and cs.CL.
% Preferred license for this version: CC BY 4.0, unless a later publisher
% requires the arXiv default non-exclusive license.

\Urlmuskip=0mu plus 2mu\relax
\captionsetup[figure]{font=small,justification=raggedright,singlelinecheck=false}
\captionsetup[table]{font=small,justification=raggedright,singlelinecheck=false}
\captionsetup[longtable]{font=small,justification=raggedright,singlelinecheck=false}
\setlength{\textfloatsep}{6pt plus 2pt minus 2pt}
\setlength{\floatsep}{6pt plus 2pt minus 2pt}
\setlength{\intextsep}{7pt plus 2pt minus 2pt}
\setlength{\LTpre}{6pt plus 2pt minus 2pt}
\setlength{\LTpost}{6pt plus 2pt minus 2pt}
\setlength{\abovecaptionskip}{3pt plus 1pt minus 1pt}
\setlength{\belowcaptionskip}{1pt plus 1pt minus 1pt}
\setlength{\parskip}{0pt}
\frenchspacing
\raggedbottom
\newcolumntype{L}[1]{>{\raggedright\arraybackslash}m{#1}}
\newcolumntype{C}[1]{>{\centering\arraybackslash}m{#1}}
\setcounter{topnumber}{4}
\setcounter{bottomnumber}{2}
\setcounter{totalnumber}{5}
\renewcommand{\topfraction}{0.92}
\renewcommand{\bottomfraction}{0.75}
\renewcommand{\textfraction}{0.06}
\renewcommand{\floatpagefraction}{0.82}
\makeatletter
\setlength{\@fptop}{0pt}
\setlength{\@fpsep}{6pt plus 1fil}
\setlength{\@fpbot}{0pt plus 1fil}
\renewcommand\section{\@startsection{section}{1}{\z@}%
  {1.75ex}%
  {0.82ex}%
  {\normalfont\Large\bfseries}}
\renewcommand\subsection{\@startsection{subsection}{2}{\z@}%
  {1.50ex}%
  {0.72ex}%
  {\normalfont\large\bfseries}}
\renewcommand\paragraph{\@startsection{paragraph}{4}{\z@}%
  {0.90ex}%
  {-0.75em}%
  {\normalfont\normalsize\bfseries}}
\makeatother
\newcommand{\PostTableHeadingSpace}{\FloatBarrier\vspace{-0.35\baselineskip}}
\newcommand{\PostFigureHeadingSpace}{\FloatBarrier\vspace{-0.35\baselineskip}}
\newcommand{\PostReferencesSpace}{\FloatBarrier\vspace{-0.28\baselineskip}}

\title{Beyond Prompting: Harness Engineering for Enterprise LLM Agents}

\author{%
  Joongho Ahn\\
  AI Leadership Research Center\\
  \texttt{joongho@ceoai.kr}
  \and
  Moonsoo Kim\thanks{Corresponding author.}\\
  AI Leadership Research Center\\
  \texttt{mskim@ceoai.kr}
}

\date{}

\begin{document}

\maketitle

\begin{abstract}
Enterprise large language model (LLM) applications are often first explored as prototypes whose behavior is carried by prompts and retrieval context. These prototypes can demonstrate useful interactions, but productization adds requirements for source boundaries, entity routing, answer contracts, and reproducible traces. We present a harness-engineering approach that reconstructs this prototype pattern into a traceable LLM-agent architecture. The method moves deterministic behavior into code, manifests, schemas, and validation artifacts, while source-backed claims remain the authority for runtime answers. We apply the approach to a public-data reference slice of five Korean corporate groups, 25 listed companies, and 113 source-backed runtime claims. The baseline passes 30/30 fixed validation-scenario contract checks, including source-reference resolution, trace preservation, answer-structure checks, and user-facing output hygiene. Runtime interface checks further exercise live filing, market, and news connections; in a separate 14-scenario orchestration check, caching and parallel source collection reduce mean measured latency from 2008.57ms to 171.14ms. The result is a reusable engineering pattern for turning exploratory enterprise LLM prototypes into auditable and extensible applications with versioned source, control, and validation artifacts.
\end{abstract}


\input{sections/01_introduction}
\input{sections/02_related_work}
\input{sections/03_method}
\input{sections/04_data_and_knowledge_base}
\input{sections/05_system_validation}
\input{sections/06_discussion}
\input{sections/07_conclusion}

\section*{Disclosures}

The study uses public and official materials only. The named corporate groups are included as a public-data engineering slice and had no sponsorship role in the study. The motivating prototype was developed during a CEO AI program, and the AI Leadership Research Center affiliation reflects the CEO AI program context; CEO AI provided no funding for the paper, and the named corporate groups had no role in study design or reporting. The system is designed for traceable briefing and source inspection, with investment-advice and investment-performance evaluation outside the study scope. Live-LLM run requirements and repository availability are described in \Cref{sec:implementation-details,sec:reproducibility}.

\appendix
\raggedbottom
\section*{Appendix}
\renewcommand{\thesubsection}{A\arabic{subsection}}
\renewcommand{\thetable}{A\arabic{table}}
\renewcommand{\thefigure}{A\arabic{figure}}
\setcounter{subsection}{0}
\setcounter{table}{0}
\setcounter{figure}{0}
\input{sections/08_appendix_scenarios}

\PostReferencesSpace
\bibliographystyle{plainnat}
\bibliography{bib/references}

\end{document}
